Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
change a few words

\noindent\textbf{Contributions}\quad In this work, we propose a framework to
perform interactive visualization of complex 3D digital structures combined with
a dynamic curvature tensor estimation. More precisely, we define a fully data
parallel process on GPU (Graphics Processor Unit) hardware to both efficiently
extract adaptive isosurface and compute per vertex curvature tensor using
Integral Invariants estimators. Hence, this system allows us to visualize
curvature tensor in real-time on large dynamic objects. Our approach combines a
GPU implementation of pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of integral
invariant curvature estimators.

@@

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching Cubes approach by \textsc{Lorensen} and
\textsc{Cline}~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by \textsc{Lengyel} \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs. 
%However, it
%was only developed on CPU to visualize in real-time static or near
%static data, combining octree with new Marching Cubes configurations
%to generate adaptive meshes. 
It combines an octree space partitioning with new Marching Cubes configuration
to generate adaptive meshes, but was only developed on the CPU to visualize
static or near static data.
In this paper we propose a full GPU pipeline
%inspired from this method.  
inspired from this method, using a GPU-friendly Lod criterion to maintain a view dependent triangulation.
%It leaves the CPU free for other tasks and avoids synchronization with the GPU.  
%Our high framerate also allows
Our high framerate allows
this method to run in real-time on fully dynamic data.  
%The triangulation is controlled by a GPU LoD criterion 
%that ensures that
%triangles project onto more than one pixel, thus removing geometrical
%aliasing.

Curvature estimation on discrete or digital surface has also been
widely investigated. In \cite{CVIU2014}, authors propose digital
versions of Integral Invariant estimators
\cite{Pottmann2007,Pottmann2009} in order to estimate the complete
curvature tensor (mean/Gaussian curvatures, principal curvatures,
principal curvature directions, normal vector field) on digital
surfaces. Such approaches are based on an integration principle using
a spherical kernel of a given radius. Additionally, authors have
demonstrated that these estimators have multigrid convergence
properties. In this article, we propose an efficient GPU
implementation of such estimators in order to visualize, in real-time,
such curvature maps and allowing us to interactively explore different
values of the spherical kernel radius.

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
    % {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    % {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    % {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    % {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are close enough. For
example, with $R=20$, the approximated visualization at $l_2$ takes only 300ms
while the $l_0$ visualization takes more than 4 seconds.

>>>>

\noindent\textbf{Contributions}\quad In this work, we propose a framework to
perform interactive visualization of complex 3D digital structures combined with
%a dynamic curvature tensor estimation. More precisely, we define a fully data
a dynamic curvature tensor estimation. We define a fully data
%parallel process on GPU (Graphics Processor Unit) hardware to both efficiently
parallel process on the GPU (Graphics Processor Unit) to both efficiently
extract adaptive isosurface and compute per vertex curvature tensor using
Integral Invariants estimators. 
%Hence, this system allows us to visualize
This system allow us to visualize
curvature tensor in real-time on large dynamic objects. Our approach combines a
GPU implementation of pointerless octrees to represent the data, an adaptive
viewpoint-dependent mesh extraction, and a GPU implementation of integral
invariant curvature estimators.

@@

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching Cubes approach by \textsc{Lorensen} and
\textsc{Cline}~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by \textsc{Lengyel} \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs. 
%However, it
%was only developed on CPU to visualize in real-time static or near
%static data, combining octree with new Marching Cubes configurations
%to generate adaptive meshes. 
It combines an octree space partitioning with new Marching Cubes configurations
to generate adaptive meshes on the CPU from 
%, but was only developed on the CPU to visualize
static or near static data.
In this paper we propose a full GPU pipeline
%inspired from this method.  
inspired from this method, 
%using a GPU-friendly Lod criterion 
to maintain a view dependent triangulation.
%It leaves the CPU free for other tasks and avoids synchronization with the GPU.  
%Our high framerate also allows
%Our high framerate allows this method to run in real-time on fully dynamic data.  
Our high framerate allows to visualize fully dynamic data in real-time.
%The triangulation is controlled by a GPU LoD criterion 
%that ensures that
%triangles project onto more than one pixel, thus removing geometrical
%aliasing.

Curvature estimation on discrete or digital surface has also been
widely investigated. In \cite{CVIU2014}, authors propose digital
versions of Integral Invariant estimators
\cite{Pottmann2007,Pottmann2009} in order to estimate the complete
curvature tensor (mean/Gaussian curvatures, principal curvatures,
principal curvature directions, normal vector field) on digital
surfaces. Such approaches are based on an integration principle using
a spherical kernel of a given radius. Additionally, authors have
demonstrated that these estimators have multigrid convergence
properties. In this article, we also propose an efficient GPU
implementation of such estimators to visualize%, in real-time,
such curvature maps in real-time and %allowing us 
to interactively change the %explore different
value of the spherical kernel radius.

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are enough close to the
$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
only 300ms while the $l_0$ visualization takes more than 4 seconds.
